Deeply Virtual Compton Scattering measurement off bound protons

### 2018-10-09 eg6-letters/incoherent/incoherent_prl.tex
some cleaning

\begin{figure}[tb]
\includegraphics[width=7.5cm]{figs/handbag_incoherent.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
   incoherent DVCS process off $^4$He, where the four-vectors of the electrons, 
   photons, and protons are denoted by $k/k^\prime$, $q/q^\prime$, and 
   $p/p^\prime$, respectively. $x+\xi$ is the nucleon’s longitudinal momentum 
   fraction carried by the struck quark, 2$\xi$ is the longitudinal momentum 
   fraction of the momentum transfer $\Delta$ ($= p - p^\prime$), and 
   $t$~($=\Delta^2$) is the squared momentum transfer between the initial and
   the final state nucleon.}
\label{fig:diags}
\end{figure}

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for the DVCS process. In the Bjorken regime, i.e, large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(p-p^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
region.  The $t$, transferred momentum squared to the recoil proton assuming an 
on-shell proton at rest, was required to be greater than a minimum allowed 
value at given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). Then, the exclusivity of the incoherent DVCS events was ensured 
by imposing constraints on the kinematical variables resulting from conserving 
the four-momentum in the reaction $ep\rightarrow e'p'\gamma$.  These 
kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray band 
   represents the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

\begin{figure}[tb]
\includegraphics[width=7.5cm]{figs/handbag_incoherent.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
   incoherent DVCS process off $^4$He, where the four-vectors of the electrons, 
   photons, and protons are denoted by $k/k^\prime$, $q/q^\prime$, and 
   $p/p^\prime$, respectively. $x+\xi$ is the nucleon’s longitudinal momentum 
   fraction carried by the struck quark, 2$\xi$ is the longitudinal momentum 
   fraction of the momentum transfer $\Delta$ ($= q - q^\prime$), and 
   $t$~($=\Delta^2$) is the squared momentum transfer between the initial and
   the final state nucleon.}
\label{fig:diags}
\end{figure}

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for the DVCS process. In the Bjorken regime, i.e, large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(q-q^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
region.  The $t$, transferred momentum squared to the recoil proton, calculated 
from 4-momentum vectors of incoming and outgoing photons, was required to be 
greater than a minimum allowed value at given Q$^2$ and 
W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We used kinematics of the photons for determining the $t$ to 
avoid uncertainty of the initial proton kinematics due to Fermi motion. Then, 
the exclusivity of the incoherent DVCS events was ensured by imposing 
constraints on the kinematical variables resulting from conserving the 
four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray band 
   represents the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
